---
title: "Astronomik Profi Grün Typ 2"
output:
  html_document:
    df_print: paged
---

```{r}
rm(list=ls())
```

```{r, message=FALSE, warning=FALSE}
library(data.table)
library(ggplot2)
library(dplyr)
```

```{r}
printf <- function(...) print(sprintf(...))
```

Read transmission data from file and preprocess
```{r}
raw <- read.csv("astronomik-green-2.csv")

data <- raw %>%
  rename(wavelength = Wavelength..nm.) %>%
  rename(transmission = X.T) %>%
  select(wavelength, transmission) %>%
  filter(complete.cases(.)) %>%
  arrange(wavelength)

print(data.table(data))
```

Transmission data wavelength range
```{r}
wavelength.range <- list(min=min(data$wavelength), max=max(data$wavelength))
wavelength.range
```

Maximum transmission within wavelength range
```{r}
index <- which.max(data$transmission)
T.max <- list(wavelength=data$wavelength[index], transmission=data$transmission[index])
T.max
```

Plot of transmission vs wavelength
```{r, echo}
ggplot(data) + 
  geom_line(aes(x=wavelength, y=transmission), color="green") +
  coord_cartesian(xlim = c(200,900), ylim=c(0,100), expand=FALSE) +
  labs(x="Wavelength [nm]", y="Transmission [%]", title="Astronomik Profi Grün 2") +
  theme_bw()
```

To calculate FWHM of the filter transmission peak I first calculate the wavelength at half maximum on the shorter wavelength side ...
```{r}
i0 <- max(which(data$transmission[1:index] < data$transmission[index]/2))
w0 <- (data$wavelength[i0] + data$wavelength[i0+1]) / 2
```

... then the wavelength at half maximum on the longer wavelength side ...
```{r}
i1 <- index + min(which(data$transmission[index:nrow(data)] < data$transmission[index]/2))
w1 <- (data$wavelength[i1] + data$wavelength[i1-1]) / 2
```

... what gives me the full with half maximum
```{r}
fwhm <- w1 - w0
fwhm
```

